---
title: "Computational Musicology Portfolio"
author: "Brian Murphy"
date: "2021"
output: 
    flexdashboard::flex_dashboard:
        storyboard: true
        theme: journal
---

```{r setup}
library(tidyverse)
library(plotly) # N.B. Requires the Cairo package
library(spotifyr)
library(compmus)
library(dplyr)
library(gridExtra)
library(ggplot2)
library(knitr)
```

Grams {.storyboard}
=========================================

### Tempogram 



***

What I find interesting about these tempograms, is that all songs have highlighted tempi above the 200 bpm, which is pretty high. By manually (https://www.justinguitar.com/tap-tempo-bpm-tool) checking the bpm of the songs, i found that the highlighted tempo is the double time of most songs. (there is only one song because my laptop couldn't handle knitting 6... I'll try and find a solution)

### Histogram of tempi


```{r}
AO_60s <- get_playlist_audio_features("", "37i9dQZF1DXaKIA8E7WcJj")
AO_70s <- get_playlist_audio_features("", "37i9dQZF1DWTJ7xPn4vNaz")
AO_80s <- get_playlist_audio_features("", "37i9dQZF1DX4UtSsGT1Sbe")
AO_90s <- get_playlist_audio_features("", "37i9dQZF1DXbTxeAdrVG2l")
AO_00s <- get_playlist_audio_features("", "37i9dQZF1DX4o1oenSJRJd")
AO_10s <- get_playlist_audio_features("", "37i9dQZF1DX5Ejj0EkURtP")
AO_decades <-
  AO_60s %>% top_n(20, track.popularity) %>%
  mutate(country = "The 60s") %>%
  bind_rows(AO_70s %>% top_n(20, track.popularity) %>% mutate(country = "The 70s")) %>%
  bind_rows(AO_80s %>% top_n(20, track.popularity) %>% mutate(country = "The 80s")) %>% 
  bind_rows(AO_90s %>% top_n(20, track.popularity) %>% mutate(country = "The 90s")) %>%
  bind_rows(AO_00s %>% top_n(20, track.popularity) %>% mutate(country = "The 00s")) %>%
  bind_rows(AO_10s %>% top_n(20, track.popularity) %>% mutate(country = "The 10s")) %>%
  mutate(
    country = fct_relevel(country, "The 10s", "The 00s", "The 90s", "The 80s", "The 70s", "The 60s")
  )

sixties_temp<- 
hist(AO_60s$tempo, main = "Tempo in the 60s",
     xlab = "Tempo",
     border="black",
     col="darkblue", 
     freq = FALSE)

seventies_temp<-
  hist(AO_70s$tempo, main = "Tempo in the 70s",  xlab = "Tempo",
       border="black", 
     col="darkblue", 
     freq = FALSE)

eighties_temp<-
   hist(AO_80s$tempo, main = "Tempo in the 80s",  
     xlab = "Tempo",
       border="black", 
     col="darkblue", 
     freq = FALSE)
     
nineties_temp<-
 hist(AO_90s$tempo, main = "Tempo in the 90s",  xlab = "Tempo",
      border="black", 
     col="darkblue", 
     freq = FALSE)

zeroes_temp<- 
   hist(AO_00s$tempo, main = "Tempo in the 00s",  xlab = "Tempo",
        border="black", 
     col="darkblue", 
     freq = FALSE)

tens_temp<-
   hist(AO_10s$tempo, main = "Tempo in the 10s", xlab = "Tempo",
        border="black", 
     col="darkblue", 
     freq = FALSE,)
```

***

Here are the histograms of tempo for each decade. I used hist instead of ggplot geom_histogram, because I couldn't get the latter to work... I want to get the top 20 tracks of each decade, make a graph with tempo on the y axis and track number on the x axis, but I can't get label=track.name to work.


### Can we find something by looking at the most populair **keys** of the last 60 years?

```{r}
AO_60s <- get_playlist_audio_features("", "37i9dQZF1DXaKIA8E7WcJj")
AO_70s <- get_playlist_audio_features("", "37i9dQZF1DWTJ7xPn4vNaz")
AO_80s <- get_playlist_audio_features("", "37i9dQZF1DX4UtSsGT1Sbe")
AO_90s <- get_playlist_audio_features("", "37i9dQZF1DXbTxeAdrVG2l")
AO_00s <- get_playlist_audio_features("", "37i9dQZF1DX4o1oenSJRJd")
AO_10s <- get_playlist_audio_features("", "37i9dQZF1DX5Ejj0EkURtP")
AO_decades <-
  AO_60s %>% top_n(20, track.popularity) %>%
  mutate(country = "The 60s") %>%
  bind_rows(AO_70s %>% top_n(20, track.popularity) %>% mutate(country = "The 70s")) %>%
  bind_rows(AO_80s %>% top_n(20, track.popularity) %>% mutate(country = "The 80s")) %>% 
  bind_rows(AO_90s %>% top_n(20, track.popularity) %>% mutate(country = "The 90s")) %>%
  bind_rows(AO_00s %>% top_n(20, track.popularity) %>% mutate(country = "The 00s")) %>%
  bind_rows(AO_10s %>% top_n(20, track.popularity) %>% mutate(country = "The 10s")) %>%
  mutate(
    country = fct_relevel(country, "The 10s", "The 00s", "The 90s", "The 80s", "The 70s", "The 60s")
  )

```


```{r}
sixties_hist<- 
hist(AO_60s$key, main = "Popular keys in the 60s",
     xlab = "key",
     border="black",
     col="darkblue", 
     freq = FALSE)

seventies_hist<-
  hist(AO_70s$key, main = "Popular keys in the 70s",  xlab = "Energy Level",
       border="black", 
     col="darkblue", 
     freq = FALSE)

eighties_hist<-
   hist(AO_80s$key, main = "Popular keys in the 80s",  
     xlab = "Energy Level",
       border="black", 
     col="darkblue", 
     freq = FALSE)
     
nineties_hist<-
 hist(AO_90s$key, main = "Popular keys in the 90s",  xlab = "Energy Level",
      border="black", 
     col="darkblue", 
     freq = FALSE)

zeroes_hist<- 
   hist(AO_00s$key, main = "Popular keys in the 00s",  xlab = "Energy Level",
        border="black", 
     col="darkblue", 
     freq = FALSE)

tens_hist<-
   hist(AO_10s$key, main = "Popular keys in the 10s", xlab = "Energy Level",
        border="black", 
     col="darkblue", 
     freq = FALSE,)
```

***

The keys are set in pitch classes, so 0=C, 1=C#/Db, 2=D etc

As you can see, the most popular key in all decades is C. The least popular key overall seems to be D. Something I don't understand is that the key only seems to go up till A#. I can't find the B...

### ### Having a deeper look at the most **positive** tunes of each decade (playlist) and see if a **chordogram** can tell us more

```{r}
circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )
```

```{r}
soy <-
  get_tidy_audio_analysis("7qiZfU4dY1lWllzX7mPBI3") %>%
  compmus_align(sections, segments) %>%
  select(sections) %>%
  unnest(sections) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

sb <-
  get_tidy_audio_analysis("0O45fw2L5vsWpdsOdXwNAR") %>%
  compmus_align(sections, segments) %>%
  select(sections) %>%
  unnest(sections) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

llvl <-
  get_tidy_audio_analysis("0Ph6L4l8dYUuXFmb71Ajnd") %>%
  compmus_align(sections, segments) %>%
  select(sections) %>%
  unnest(sections) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

wos <-
  get_tidy_audio_analysis("05wIrZSwuaVWhcv5FfqeH0") %>%
  compmus_align(sections, segments) %>%
  select(sections) %>%
  unnest(sections) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

raran <-
  get_tidy_audio_analysis("6KTv0Z8BmVqM7DPxbGzpVC") %>%
  compmus_align(sections, segments) %>%
  select(sections) %>%
  unnest(sections) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

opw <-
  get_tidy_audio_analysis("48i055G1OT5KxGGftwFxWy") %>%
  compmus_align(sections, segments) %>%
  select(sections) %>%
  unnest(sections) %>%
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

```

```{r}
plotA <-
soy %>% 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "", title = "Shape Of You")

plotB <-
sb %>% 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "", title = "SexyBack")

plotC <-
llvl %>% 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "", title = "Livin la Vida Loca")

plotD <-
wos %>% 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "", title = "Walking On Sunshine")

plotE <-
raran %>% 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "", title = "Rock And Roll All Nite")

plotF <-
opw %>% 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "", title = "Oh, Pretty Woman")

grid.arrange(plotA,plotB,plotC,plotD,plotE,plotF, nrow=2)
```

```{r}
AO_decades %>% 
    count(key_mode, sort = TRUE) %>% 
    head(5) %>%
  kable()
    
```


***

I seems as if the distinctness between notes in music has gotten bigger through the years? I have the same cluttered problem here as a do with the ceptrograms...


### Having a deeper look at the most **positive** tunes of each decade (playlist) and see if a **cepstrogram** can tell us more

```{r}
SOY <-
  get_tidy_audio_analysis("7qiZfU4dY1lWllzX7mPBI3") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

SB <-
  get_tidy_audio_analysis("0O45fw2L5vsWpdsOdXwNAR") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

LlVL <-
  get_tidy_audio_analysis("0Ph6L4l8dYUuXFmb71Ajnd") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

WOS <-
  get_tidy_audio_analysis("05wIrZSwuaVWhcv5FfqeH0") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

RARAN <-
  get_tidy_audio_analysis("6KTv0Z8BmVqM7DPxbGzpVC") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

OPW <-
  get_tidy_audio_analysis("48i055G1OT5KxGGftwFxWy") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )


```

```{r}

plot1 <-
SOY %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, title = "Shape Of You", fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

plot2<- 
SB %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, title = "SexyBack", fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

plot3<- 
LlVL %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, title = "Livin' la Vida Loca", fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

plot4<- 
WOS %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, title = "Walking On Sunshine", fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

plot5<- 
RARAN %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, title = "Rock And Roll All Nite", fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

plot6<- 
OPW %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, title = "Oh, Pretty Woman", fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

grid.arrange(plot1,plot2,plot3,plot4,plot5,plot6, nrow=2, ncol=3)

```

***

Okay so I managed to get the grams next to each other, but they're very cluttered... Does someone have a solution for this? I've tried random stuff with nrow and ncol but it didn't help. 

Introduction {.storyboard}
=========================================

### The Happiest of the Decades 

Throughout the decades we have seen happier and sadder times. Each decade has been marked by the tough times and the good times, as are we. Music has long been a means of expression for human beings, in both listening as playing. So maybe music can tell us more about the emotions of a decade's zeitgeist, which brings me to my question; which decade was the happiest, and what can the popular music released in that decade tell us about the collective happiness?

Overview {.storyboard}
=========================================

### Emotional Stats

```{r happy}
AO_60s <- get_playlist_audio_features("", "37i9dQZF1DXaKIA8E7WcJj")
AO_70s <- get_playlist_audio_features("", "37i9dQZF1DWTJ7xPn4vNaz")
AO_80s <- get_playlist_audio_features("", "37i9dQZF1DX4UtSsGT1Sbe")
AO_90s <- get_playlist_audio_features("", "37i9dQZF1DXbTxeAdrVG2l")
AO_00s <- get_playlist_audio_features("", "37i9dQZF1DX4o1oenSJRJd")
AO_10s <- get_playlist_audio_features("", "37i9dQZF1DX5Ejj0EkURtP")
AO_decades <-
  AO_60s %>% top_n(20, track.popularity) %>%
  mutate(country = "The 60s") %>%
  bind_rows(AO_70s %>% top_n(20, track.popularity) %>% mutate(country = "The 70s")) %>%
  bind_rows(AO_80s %>% top_n(20, track.popularity) %>% mutate(country = "The 80s")) %>% 
  bind_rows(AO_90s %>% top_n(20, track.popularity) %>% mutate(country = "The 90s")) %>%
  bind_rows(AO_00s %>% top_n(20, track.popularity) %>% mutate(country = "The 00s")) %>%
  bind_rows(AO_10s %>% top_n(20, track.popularity) %>% mutate(country = "The 10s")) %>%
  mutate(
    country = fct_relevel(country, "The 10s", "The 00s", "The 90s", "The 80s", "The 70s", "The 60s")
  )

  


  
  happy_stats <-
  AO_decades %>%  
  ggplot(                          # Set up the plot.
    aes(
      x = valence,
      y = track.popularity,
      colour = mode,
      size = danceability,
      label = track.name           # Labels will be interactively visible.
    )
  ) +
  geom_point(shape = ".") +                   # Scatter plot.
  geom_rug(size = 0.1) +           # Add 'fringes' to show data distribution.
  facet_wrap(~country) +           # Separate charts per country.
  scale_x_continuous(              # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),        # Use grid-lines for quadrants only.
    minor_breaks = NULL            # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(              # Fine-tune the y axis in the same way.
    limits = c(60, 90),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_viridis_c(          # Use the cividis palette
    option = "E",                  # Qualitative set.
    alpha = 0.8,                   # Include some transparency
    guide = "none"
  ) +
  scale_size_continuous(           # Fine-tune the sizes of each point.
    guide = "none"                # Remove the legend for size.
  ) +
  theme_classic() +                  # Use a simpler theme.
  labs(                            # Make the titles nice.
    x = "Valence",
    y = "Popularity"
  )
ggplotly(happy_stats)
```

***

These graphs show the valence (x axis) and the [popularity (y axis) of Spotify's own "All Out" playlists of each decade from the 60s up till the 10s. The size of the dots indicates the danceability and the colour indicates the mode (major/minor) of the song, 1 for major, 0 for minor.


### Conclusions I do not have yet

- in modern music more minor
- 00s more danceable?
- 